Gravitational wave sources in our Galactic backyard: Predictions for BH and NS binaries in LISA

### 2021-07-28 paper/tex/sections/methods.tex
update galaxy diagram with new bulge

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{1_galaxy_diagram.png}
    \caption{A schematic illustrating how we create a mock Milky Way galaxy. The left panel illustrates the different model aspects: star formation history of 3 galactic components (individually shown in the dotted lines), spatial distribution at birth, age-metallicity-radius relation, and vertical distribution.
    On the right, we show an example instance of the Milky Way with $250000$ binaries shown as points colour coded by metallicity. The top panel shows a side-on view and the bottom panel shows a face-on view.}
    \label{fig:galaxy_schematic}
\end{figure*}

>>>>

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{1_galaxy_diagram.png}
    \caption{A schematic illustrating how we create a mock Milky Way. The left side illustrates the different model aspects: star formation history of 3 galactic components (individually shown in the dotted lines), spatial distribution at birth, metallicity-radius-time relation, and vertical distribution.
    On the right, we show an example instance of the Milky Way with $250000$ binaries shown as points colour coded by metallicity. The top panel shows a side-on view and the bottom panel shows a face-on view.}
    \label{fig:galaxy_schematic}
\end{figure*}
